Optimal Duplicate Detection in a Sliding Window

### 2020-03-27 qhtv2.tex
esthétique

		\State\Return filter
		\EndFunction 
		\item[]
	\end{algorithmic}

	\begin{algorithmic}[1]
	\Function{Lookup}{$e$}
		\If{$D[h(e)] > 0$}
		\State \Return \DUPLICATE
		\EndIf
		\State \Return \UNSEEN
	\EndFunction
	\item[]
	\end{algorithmic}

@@

A quick description of the Compact Short Hash Filter (CSHF) is given in Algorithm~\ref{alg:CSHF}.

\begin{algorithm}[]
	\caption{CSHF, Lookup and Insert}\label{alg:CSHF}

	\begin{algorithmic}[1]
		\Function{Setup}{$\mathcal M, w$}
		\Comment $M$ is the available memory, $w$ the size of the sliding window
		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
		\State\Return filter
		\EndFunction 
		\item[]
	\end{algorithmic}

	\begin{algorithmic}[1]
		\Function{Lookup}{$e$}
		\State \Return $h(e) \in Q$ 
		\EndFunction
		\item[]
	\end{algorithmic}

	\begin{algorithmic}[1]
		\Function{Insert}{$e$}
		\Comment Same as SHF, but removing all instructions about its dictionnary $D$.
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

\begin{figure}
	\input{graphs/w_opt_shf.tex}
	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 50\% ($\pm 0.001$), for various values of $M$.}\label{fig:w_opt}
\end{figure}

@@

\begin{figure}[!ht]
	\centering
	\input{graphs/stream_size_qht.tex}
	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
\end{figure}

@@

\end{tikzpicture}
	\caption{Comparing performances of various filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
\end{figure*}

\end{document}

>>>>

		\State\Return filter
		\EndFunction 
%		\item[]
	\end{algorithmic}

	\begin{algorithmic}[1]
	\Function{Lookup}{$e$}
		\If{$D[h(e)] > 0$}
		\State \Return \DUPLICATE
		\EndIf
		\State \Return \UNSEEN
	\EndFunction
%	\item[]
	\end{algorithmic}

@@

A quick description of the Compact Short Hash Filter (CSHF) Setup function is given in Algorithm~\ref{alg:CSHF}. The other functions are similar to the ones of Algorithm~\ref{alg:SHF}, removing all references to the dictionary.

\begin{algorithm}[]
	\caption{CSHF, Setup}\label{alg:CSHF}

	\begin{algorithmic}[1]
		\Function{Setup}{$\mathcal M, w$}
		\Comment $M$ is the available memory, $w$ the size of the sliding window
		\State $h \gets$ hash function of codomain size $\lfloor \frac Mw \rfloor$
		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
		\State\Return filter
		\EndFunction 
		\item[]
	\end{algorithmic}
%	
%	\begin{algorithmic}[1]
%		\Function{Lookup}{$e$}
%		\State \Return $h(e) \in Q$ 
%		\EndFunction
%		\item[]
%	\end{algorithmic}
%	
%	\begin{algorithmic}[1]
%		\Function{Insert}{$e$}
%		\Comment Same as SHF, but removing all instructions about its dictionnary $D$.
%		\EndFunction
%	\end{algorithmic}
\end{algorithm}

@@

\begin{figure}
	\input{graphs/w_opt_shf.tex}
	\caption{Value $w_{max}$ for which SHF and CSHF reach an error of 0.5 ($\pm 0.001$), for various values of $M$.}\label{fig:w_opt}
\end{figure}

@@

\begin{figure*}[!ht]
	\centering
	\input{graphs/stream_size_qht.tex}
	\caption{Error rate for queuing QHT ($L = 10$, $M = 10^5$, $|\Gamma| = 2^{16}$) with streams of size $10^5$ to $10^8$.}\label{fig:strangess}
\end{figure*}

@@

\end{tikzpicture}
	\caption{Comparing performances of various filters, in `vanilla' setting or when placed in our queueing structure.}\label{fig:appendix_improvement}
\end{figure*}
\end{document}
